Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-13 manuscript/manuscript.tex
Start writing sine density subsection

Having chosen values of $D$ equal to the ones obtained for the linear density case, we
are free to explore the integration error as a function of $\delta$ in more detail and
how it varies for different values of $b$ (Eq.~\ref{eq:density-exp}).
Now we perform the error calculations for the every grid detailed in
Table~\ref{tab:grids} and for the 20 spherical shells models detailed in
Table~\ref{tab:tess-collections}.
The calculations are repeated for different values of $b$ (1, 2, 5, 10, 30, 100) to
examine the error variation with the sharpness of the density function.
Because larger $\delta$ values result in fewer tesseroid divisions,
our intention is to find the highest value of $\delta$ whose numerical error is bellow
the $0.1\%$ threshold.

@@

@@

>>>>

Having chosen values of $D$ equal to the ones obtained for the linear density case, we
are free to explore the integration error as a function of $\delta$ in more detail and
how it varies for different values of $b$ (Eq.~\ref{eq:density-exp}).
Now we perform the error calculations for values of delta ranging from $10^{-3}$ to
$10^{1}$, for every grid detailed in Table~\ref{tab:grids} and for the 20 spherical
shells models detailed in Table~\ref{tab:tess-collections}.
The calculations are repeated for different values of $b$ (1, 2, 5, 10, 30, 100) to
examine the error variation with the sharpness of the density function.
Because larger $\delta$ values result in fewer tesseroid divisions,
our intention is to find the highest value of $\delta$ whose numerical error is bellow
the $0.1\%$ threshold.

@@

\subsection{Trigonometric Density}

So far we have tested the density-based discretization algorithm against linear and
exponential density functions.
Nevertheless, this new algorithm is well suited to accurately reproduce the
gravitational fields of tesseroids with more complex continuous functions, like
non-monotonic or with one or more inflection points.
Although such density functions are very rare (or maybe even non-existent) between
geological structures, we want to subject the density-based algorithm to such cases in
order to show that it can solve more complex situations other than linear and
exponential functions.

We will consider spherical shells with a trigonometric density defined as follows:

\begin{equation}
    \rho(r') = A \sin \left( 2 \pi b \frac{r' - R}{T} \right) + A,
    \label{eq:sine-density}
\end{equation}

\noindent where $A$ is a constant, $T$ is the thickness of the shell, $R$ is the mean
Earth radius and $b$ is a dimensionless constant that regulates how many periods of the
trigonometric function are included inside the inner and outer radii.
For this analysis we will use values of $b$ equal to 1, 2, 5 and 10
(Fig.~\ref{fig:sine-densities}).
We shift the sine function in order to prevent near zero values of the potential and the
$g_z$.

We compute the relative difference between the numerical and analytical results for the
gravitational potential ($V$) and the $g_z$ of spherical shells with this kind of
sinusoidal density function.
The analytical solution for the potential $V$ can be found on Appendix~\ref{sec:shell}.
The gravitational fields are computed on every grid detailed in Table~\ref{tab:grids}
and making use of the spherical shells defined on Table~\ref{tab:tess-collections}.
Each shell is assigned with different sinusoidal density functions by changing the
values of $b$ in Eq.~\ref{eq:sine-density} (Fig.~\ref{fig:sine-densities}).

@@

\subsection{Sinusoidal density}

For an sinusoidal density function

\begin{equation}
    \rho(r') = A \sin ( k (r' - R)),
\end{equation}

\begin{equation}
    \begin{split}
    V_\text{sine}(r) = \frac{4\pi G}{r} \frac{A}{k^3} \Big[
    & (2 - k^2 R_2^2) \cos(k(R_2 - R)) + 2 k R_2 \sin(k(R_2 - R)) -
    & (2 - k^2 R_1^2) \cos(k(R_1 - R)) - 2 k R_1 \sin(k(R_1 - R))
        \Big]
    \end{split}
\end{equation}
